Exploring variables in the data

### 2017-07-28 Hours.Rmd
updated total hours
reorganized files and code, made code more reproducible, updated hours, deleted files
finished literature reviews, updated hours
finished work with tags, updated hours, tweaked functions/other files

>> __Total Hours: 89.08__

>>>>

7/21/2017 | 4.5 | 7:00-11:30AM | Re-organized summary statistics
7/21/2017 | 6 | 3:30-9:30PM | Continued to re-organize, wrote functions/rewrote parts of code
7/22/2017 | 2 | 10:00-12:00PM | Re-organzied freq words file
7/22/2017 | 4 | 3:00-7:00PM | Literature reviews
7/24/2017 | 1.5 | 8:30-10:00AM | Finished literature reviews
7/24/2017 | 3 | 1:00-4:00PM | Explored tags, created new variables
7/24/2017 | 3 | 6:00-9:00PM | Tried to create tag frequency variable, ran into problems, looked into creating own r package
7/25/2017 | 2 | 9:00-11:00AM | Continued to work analyze tag variable
7/25/2017 | 3 | 1:00-4:00PM | Wrote the code for tag variables, tried to fix Java problem
7/27/2017 | 7 | 12:00-7:00 | Met with the Data Specialist to discuss data visualization ideas, finished working with tags, started with textual features of the data
>> __Total Hours: 133.08__

### 2017-07-28 freq_words.Rmd
finished work with tags, updated hours, tweaked functions/other files

#function to plot survival curves with ggplot
plot_surv <- function(survfit, data, ...) {
  library(ggfortify)
  library(directlabels)

@@

  if (!("strata" %in% names(df))) {
    ggplot(df, aes(x = time, y = surv)) + 
    geom_line() + 
    scale_y_continuous("Survival Probability") +
    scale_x_continuous("Time")
    ggtitle("Survival Curve")
  }

  if ("strata" %in% names(df)) {
    ggplot(df, aes(x = time, y = surv, color = strata)) + 
      geom_line() + 
      scale_y_continuous("Survival Probabilities") +
      scale_x_continuous("Time") + 
      ggtitle("Survival Curves") + 
      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
  }
}
```

>>>>

#function to plot survival curves with ggplot
plot_surv <- function(survfit, data, xlim = NULL) {
  library(ggfortify)
  library(directlabels)

@@

  if (missing(xlim)) {

    if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time")
          ggtitle("Survival Curve")
        }
    if ("strata" %in% names(df)) {
      ggplot(df, aes(x = time, y = surv, color = strata)) + 
        geom_line() + 
        scale_y_continuous("Survival Probabilities") +
        scale_x_continuous("Time") + 
        ggtitle("Survival Curves") + 
        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
    }
  } else {

      if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time", limits = xlim)
          ggtitle("Survival Curve")
      }

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

### 2017-07-28 functions.Rmd
finished work with tags, updated hours, tweaked functions/other files

```{r}
setup <- function() {
  dir <- file.path(getwd(),"data")
  out <- read.csv(file.path(dir, "answers_data.csv"))

  library(dplyr)
  out_english <- out %>% 
                  tbl_df() %>%
                  filter(langid == "en")

  out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
  empty <- which(is.na(out_english$time_until_answer))
  for (i in empty) {
    out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}
}

```

```{r}

plot_surv <- function(survfit, data) {

  library(ggfortify)
  library(directlabels)

@@

  if (!("strata" %in% names(df))) {
    ggplot(df, aes(x = time, y = surv)) + 
    geom_line() + 
    scale_y_continuous("Survival Probability") +
    scale_x_continuous("Time")
    ggtitle("Survival Curve")
  }

  if ("strata" %in% names(df)) {
    ggplot(df, aes(x = time, y = surv, color = strata)) + 
      geom_line() + 
      scale_y_continuous("Survival Probabilities") +
      scale_x_continuous("Time") + 
      ggtitle("Survival Curves") + 
      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
  }
}
```

>>>>

```{r}
library(dplyr)
library(ggfortify)
library(directlabels)
library(tm)
library(qdap)
```

```{r}
#imports data set, includes only questions in English, creates time_until_answer (in hrs)
setup <- function() {
  dir <- file.path(getwd(),"data")
  out <- read.csv(file.path(dir, "answers_data.csv"))

  out_english <- out %>% 
                  tbl_df() %>%
                  filter(langid == "en")

  out_english$time_until_answer <- (out_english$first_answer_date - out_english$post_date)/3600
  empty <- which(is.na(out_english$time_until_answer))
  for (i in empty) {
    out_english$time_until_answer[i] <- (out_english$download_date[i] - out_english$post_date[i])/3600
}
}
```

```{r}
#function to plot survfit objects
#input: survfit object, data, optional x-axis limits
plot_surv <- function(survfit, data, xlim) {

@@

  if (missing(xlim)) {

    if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time")
          ggtitle("Survival Curve")
        }
    if ("strata" %in% names(df)) {
      ggplot(df, aes(x = time, y = surv, color = strata)) + 
        geom_line() + 
        scale_y_continuous("Survival Probabilities") +
        scale_x_continuous("Time") + 
        ggtitle("Survival Curves") + 
        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
    }
  } else {

      if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time", limits = xlim)
          ggtitle("Survival Curve")
      }

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

```{r}
#function to clean corpus
clean_corpus <- function(corpus){

  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

#returns a data frame of words and frequencies sorted by most to least frequent
#input: character vector of words, n is optional (to output top n most frequent words)
freq_terms <- function(vec, n) {

  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  freq_df <- data.frame(word = names(freq), frequency = unname(freq))

  if (missing(n)) {
    return(freq_df)
  }
  else {
    return(freq_df[1:n,])
  }
}
```

### 2017-07-28 variable_exploration.Rmd
finished work with tags, updated hours, tweaked functions/other files

```{r, function to plot KM curves with ggplot, include = FALSE}
#function to plot KM_curves with ggplot (use when it's hard to read ggsurvplot output)

plot_surv <- function(survfit, data, ...) {
  library(ggfortify)
  library(directlabels)

@@

  if (!("strata" %in% names(df))) {
    ggplot(df, aes(x = time, y = surv)) + 
    geom_line() + 
    scale_y_continuous("Survival Probability") +
    scale_x_continuous("Time")
    ggtitle("Survival Curve")
  }

  if ("strata" %in% names(df)) {
    ggplot(df, aes(x = time, y = surv, color = strata)) + 
      geom_line() + 
      scale_y_continuous("Survival Probabilities") +
      scale_x_continuous("Time") + 
      ggtitle("Survival Curves") + 
      geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
  }
}

>>>>

```{r, functions, include = FALSE}
#function to plot KM_curves with ggplot (use when it's hard to read ggsurvplot output)
#takes survfit object, data set to work with, and optional x-axis limits as input, outputs ggplot KM curves

plot_surv <- function(survfit, data, xlim = NULL) {
  library(ggfortify)
  library(directlabels)

@@

  if (missing(xlim)) {

    if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time")
          ggtitle("Survival Curve")
        }
    if ("strata" %in% names(df)) {
      ggplot(df, aes(x = time, y = surv, color = strata)) + 
        geom_line() + 
        scale_y_continuous("Survival Probabilities") +
        scale_x_continuous("Time") + 
        ggtitle("Survival Curves") + 
        geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
    }
  } else {

      if (!("strata" %in% names(df))) {
        ggplot(df, aes(x = time, y = surv)) + 
          geom_line() + 
          scale_y_continuous("Survival Probability") +
          scale_x_continuous("Time", limits = xlim)
          ggtitle("Survival Curve")
      }

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}

#function to output logrank test and survival curves
#takes in Surv object, data set, and categorical variable 
# surv_analysis <- function(surv_object, group, data, xlim) {
#   
#   survdiff(surv_object ~ group, data)
#   
#   if (missing(xlim)) {
#     KM <- survfit(surv_object ~ group, data)
#     plot_surv(KM, data)
#   } else {
#     KM <- survfit(surv_object ~ group, data)
#     plot_surv(KM, data, xlim)
#   }
# }
# surv_analysis(surv_object, group = "category", data = out_english)
